---
title: "Data PreProcessing"
author: "Anna Lizarov"
date: "June 19, 2019"
output: html_document
---

# Libraries
```{r}
library(dplyr)
library(tidyr)
library(stringr)
```

# Datasets
```{r}
# Quiz 1
q1 <- read.csv("HUDK 5053 Online Class Activity Quiz 1_June 18, 2019_16.39.csv", header=TRUE, na.strings = "")
# Quiz 2
q2 <- read.csv("HUDK 5053 Online Class Activity Quiz 2_June 18, 2019_16.47.csv", header=TRUE, na.strings = "")
# Quiz 3
q3 <- read.csv("HUDK 5053 Online Class Activity Quiz 3_June 18, 2019_16.48.csv", header=TRUE, na.strings = "")
# Quiz 4
q4 <- read.csv("HUDK 5053 Online Class Activity Quiz 4_June 18, 2019_16.40.csv", header=TRUE, na.strings = "")
```

# Clean up
```{r}
q.list = list(q1,q2,q3,q4)
q <-lapply(q.list, function(x){
  x <- x[-(1:2),]
  x <- select(x, -c(StartDate,EndDate, Status, IPAddress, ResponseId, LocationLatitude, LocationLongitude, DistributionChannel, RecordedDate, ExternalReference, RecipientLastName, RecipientFirstName, RecipientEmail))
  return(x)
  })
# save dfs to csv with similar lapply-call:
n <- 1:length(q)
lapply(n, function(ni) {
               write.csv(file = paste("Quiz_", ni, ".csv", sep = ""), 
               q[ni], row.names = F)
               }
       )
```

# Recoding the first quiz
```{r}
Q1 = read.csv("Quiz_1.csv", header=TRUE, na.strings = "")
```

## Recoding the variables
```{r}
Q1$Q1 = as.character(Q1$Q1)
Q1$Q1[Q1$Q1 == "Xt2213"] = "xt2213"
Q1$Q1Q6 = ifelse(Q1$Q1Q6 == "Yes", 1,0)
Q1 <- select(Q1, -c(Q2, Q3))
```

# Recoding the second quiz 
```{r}
Q2 = read.csv("Quiz_2.csv", header=TRUE, na.strings = "")
```

## Recoding the variables
```{r}
Q2$Q2Q4 = ifelse(Q2$Q2Q4 == "For pronunciation and distinguishing words", 1, 0)
Q2$Q2Q5 = ifelse(Q2$Q2Q5 == "33", 1, 0)
Q2$Q2Q6 = ifelse(Q2$Q2Q6 == "Modifies the pronunciation of the preceding consonant by making it soft", 1, 0)
Q2$Q2Q7 = ifelse(Q2$Q2Q7 == "Whether the noun is singular or plural and its gender", 1, 0)
```

## Recalculating the scores
```{r}
Q2$Q2Score = rowSums(Q2[,(8:11)], na.rm=TRUE)
Q2$Q2Alphabet = rowSums(Q2[,(9:10)], na.rm=TRUE)
Q2$Q2IntrotoRussian = rowSums(Q2[,c(8:9,11)], na.rm=TRUE)
Q2$Q2PersonalPronounsPoss = Q2[,11]
Q2 <- select(Q2, -c(SC0, SC1,SC2,SC3, Q2,Q3))
```

## Calculating the percentages
```{r}
Q2 <- Q2 %>% mutate(Q2Score_pct =(Q2Score/4)*100, Q2Alphabet_pct = (Q2Alphabet/2)*100, Q2IntrotoRussian_pct = (Q2IntrotoRussian/3)*100,Q2PersonalPronounsPoss_pct=(Q2PersonalPronounsPoss*100)) 
```

# Recoding the third quiz
```{r}
Q3 = read.csv("Quiz_3.csv", header=TRUE, na.strings = "")
```

## Recoding the variables
```{r}
Q3$Q3Q4 = gsub(".*\\[", "", Q3$Q3Q4)
Q3$Q3Q4 = ifelse(Q3$Q3Q4 == "vi]", 1,0)
```

## Recalculating the scores
```{r}
Q3$Q3Score = Q3$Q3Q4
Q3$Q3Greetings = Q3$Q3Q4
Q3$Q3PersonalPronounsPoss = Q3$Q3Q4
Q3 <- select(Q3, -c(SC0, SC1,SC2,Q2,Q3))
```

## Calculating the percentages
```{r}
Q3 <- Q3 %>% mutate(Q3Score_pct = Q3$Q3Score*100, Q3Greetings_pct = Q3Greetings*100, Q3PersonalPronounsPoss_pct = Q3PersonalPronounsPoss*100 )
```

# Recoding the fourth quiz
```{r}
Q4 = read.csv("Quiz_4.csv", header=TRUE, na.strings = "")
Q4
```

## Recoding the variables
```{r}
Q4$Q4Q4 = ifelse(Q4$Q4Q4 == "TRUE", 1, 0)
Q4$Q4Q5 = ifelse(Q4$Q4Q5 == "FALSE", 1, 0)
Q4$Q4Q6 = ifelse(Q4$Q4Q6 == "TRUE", 1, 0)
Q4$Q4Q7 = ifelse(Q4$Q4Q7 == "FALSE", 1, 0)
Q4$Q4Q8 = ifelse(Q4$Q4Q8 == "TRUE", 1, 0)
Q4$Q4Q9 = gsub(".*\\[", "", Q4$Q4Q9)
Q4$Q4Q9 = ifelse(Q4$Q4Q9 == "leto]", 1,0)
Q4$Q4Q10 = ifelse(Q4$Q4Q10 == "Yes", 1, 0)
Q4$Q4Q11 = ifelse(Q4$Q4Q11 == "Yes", 1, 0)
Q4$Q4Q12 = ifelse(Q4$Q4Q12 == "Yes", 1,ifelse(Q4$Q4Q12 == "Maybe", 2, 0))
Q4$Q4Q14 = ifelse(Q4$Q4Q14 == "Yes", 1, 0)
```

## Recalculating the scores
```{r}
Q4$Q4Score = rowSums(Q4[,(8:13)])
Q4$Q4Alphabet = Q4$Q4Q5
Q4$Q4Greetings = Q4$Q4Q7
Q4$Q4IntrotoRussian = rowSums(Q4[, c(8,11,12)])
Q4$Q4PersonalPronounsPoss = Q4$Q4Q6
Q4$Q4Calendar = rowSums(Q4[,(12:13)])
```

## Calculating the percentages
```{r}
Q4 <- Q4 %>% mutate(Q4Score_pct = (Q4Score/6)*100,Q4Alphabet_pct=Q4Alphabet*100, Q4Greetings_pct = Q4Greetings*100, Q4IntrotoRussian_pct=(Q4IntrotoRussian/3)*100, Q4PersonalPronounsPoss_pct = Q4PersonalPronounsPoss*100, Q4Calendar_pct = (Q4Calendar/2)*100)
Q4 <- select(Q4, -c(SC0, SC1,SC2,SC3,SC4, Q2,Q3))
```

# Saving as CSV files
```{r}
Q.list = list(Q1,Q2,Q3,Q4)
# save dfs to csv with similar lapply-call:
n <- 1:length(Q.list)
lapply(n, function(ni) {
               write.csv(file = paste("Quiz_", ni, "_(processed)", ".csv", sep = ""), 
               Q.list[ni], row.names = F)
               }
       )
```

# Unifying all of the dataframes into one
```{r}
Q <- merge(Q1,Q2, by = "Q1", all=TRUE)
Q <- merge(Q,Q3, by = "Q1", all=TRUE)
Q <-merge(Q,Q4, by= "Q1", all=TRUE)
# write CSV
write.csv(Q, file = "Full_Quiz_Dataset.csv")
```

